Safe and Robust Formal Synthesis of Digital Controllers for Continuous Plants

### 2018-02-19 automatica/paper.tex
abstract + comments

\begin{abstract}                          % Abstract of not more than 200 words.
\textcolor{red}{Cristina: Can you please write an initial version of the abstract.}
\end{abstract}

@@

\addtodo{change this}
For this purpose, we leverage a very recent step-change in the automation and
scalability of \emph{program synthesis}.  %% Program synthesis engines use a
%% specification as the starting point, and subsequently generate a sequence of
%% candidate programs from a given template.  The candidate programs are
%% iteratively refined to eventually satisfy the specification.
Program
synthesizers implementing Counter-Example Guided Inductive Synthesis
(CEGIS)~\cite{DBLP:conf/asplos/Solar-LezamaTBSS06} are now able to generate
programs for highly non-trivial specifications with a very high degree of
automation.  Modern synthesis engines combine automated testing, genetic
algorithms, and SMT-based automated
reasoning~\cite{DBLP:journals/corr/AlurFSS16a, DBLP:conf/lpar/DavidKL15}.

@@

%% Using state of the art verifiers, we evaluate these models against
%% automatically synthesised controllers using CEGIS-based synsthesis that
%% incorporate the above mentioned artifacts in different models of
%% Single-Input/Single-Output (SISO) systems.
\addtodo{I guess this should be two}
We offer three modes of
operation that address different aspects of the problem.

@@

In summary, this paper makes the following original contributions.
%
\begin{enumerate}

>>>>

\begin{abstract}                          % Abstract of not more than 200 words.
%\textcolor{red}{Cristina: Can you please write an initial version of the abstract.}
We present a sound and automated approach to synthesizing safe,
digital controllers for physical plants represented as linear,
time-invariant models. Models are defined as differential equations
with inputs, evolving over a continuous state space. The synthesis
accounts for errors caused by the digitization effects introduced by
the controller. Our approach uses counterexample-guided inductive
synthesis (CEGIS): an inductive generalisation phase produces a
possible solution that is known to stabilize the system but that may
not be safe for all initial conditions. Safety is then verified either
via BMC or abstract acceleration; if the verification step fails, a
counterexample is provided to the inductive generalisation and the
process iterates until a safe controller is obtained.  We demonstrate
the practical value of this approach by automatically synthesizing
safe controllers for physical plant models from the digital control
literature.
\end{abstract}

@@

\addtodo{CD: change this}
For this purpose, we leverage a very recent step-change in the automation and
scalability of \emph{program synthesis}.  %% Program synthesis engines use a
%% specification as the starting point, and subsequently generate a sequence of
%% candidate programs from a given template.  The candidate programs are
%% iteratively refined to eventually satisfy the specification.
Program
synthesizers implementing Counter-Example Guided Inductive Synthesis
(CEGIS)~\cite{DBLP:conf/asplos/Solar-LezamaTBSS06} are now able to generate
programs for highly non-trivial specifications with a very high degree of
automation.  Modern synthesis engines combine automated testing, genetic
algorithms, and SMT-based automated
reasoning~\cite{DBLP:journals/corr/AlurFSS16a, DBLP:conf/lpar/DavidKL15}.

@@

%% Using state of the art verifiers, we evaluate these models against
%% automatically synthesised controllers using CEGIS-based synsthesis that
%% incorporate the above mentioned artifacts in different models of
%% Single-Input/Single-Output (SISO) systems.
\addtodo{CD: I guess this should be two}
We offer three modes of
operation that address different aspects of the problem.

@@

\addtodo{CD: the novelty compared to CAV'17 needs to be clarified}
In summary, this paper makes the following original contributions.
%
\begin{enumerate}
